The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-04-10 manuscript/manuscript.qmd
Woohoo major final edits for MPSA panel

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
date: "2023-04-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we measure the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas. We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are allowed to work in by the registration documentation. China provides an excellent setting for testing the "closing space" and "changing space" theoretical understanding because the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
bibliography: references.bib
link-citations: true
---

@@

# Introduction

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss:2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*). An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a]. China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a recent global wave of legal restrictions on INGOs. As an authoritarian jurisdiction with a growing nonprofit sector, the Chinese model of implementing restrictive laws for INGOs has great implications for scholarly understanding of the dynamics of how such laws are used as policy tools to harness INGOs in practice. The purpose of this study is to empirically examine how the ONGO Law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we intent to inquire into a more comprehensive and data-based picture of the operational space for INGOs. It will also test out the evolving theory of the "closing space" or "changing space" for INGOs hold true in a representative empirical setting of the mainland China.

INGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009]. Before the promulgation of the ONGO Law, the regulation of INGOs in China was obscure [Shieh:2018; Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China [@YeHuang:2018].

Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011]. They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees. However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs. Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021]. Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investors' right to investment return.

The legal framework governing ONGOs was overhauled by the Chinese ONGO Law. The new law applies to all Overseas (including Hong Kong, Macau and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of Economic Development, Education, Science, Technology, Culture, Public Health, Sports, Environment Protection, Poverty Alleviation, and Disaster Relief etc. (Article 3). In other words, after the Overseas NGOs became effective, any nonprofit activities conducted by those ONGOs that cannot successfully obtaining proper legal authorization according to the law will be deemed illegal. Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs or filing information for documentation of temporary activities with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authority for ONGOs designated by the law. Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year.

This paper studies the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between INGO issue areas and the composition of successful RO registration and the operational space granted. Registering RO under the ONGO Law requiring the consent of a Chinese professional supervisory unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus. And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. Therefore, the composition of the successfully registered RO inform us whether ROs working on different issue areas have varied level of difficulty in obtaining legal status. Moreover, We measure the later with a proxy of the number of provinces that the ROs are authorized to operate. Specifically, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18). Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all. We use the number of provinces that ROs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the empirical understanding that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as larger as possible. [@Li:2020]

# Literature and Theoretical Background

## Literature on Closing Space for INGOs

Contentiousness, regime stability, other reasons (to add studies on this construct globally)

## Literature on differenciated attitudes towards INGOs (as reveal in implementation)

@@

*de jure* vs. *de facto* difference "represents a bureaucratic form of repression" [@ChaudhryHeiss:2022]

The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss:2022; @Carothers:2016].  Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies [@Jia:2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

Based on extant literature and theoretical understanding, we hypothesize that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in. Since the level of contentious is also manifested by the level of difficulty they face while seeking lawful registration. We also hypothesize that large operational space of INGOs is negatively associated the time elapsed since the law took effect when they successfully got registered.

The follow section is structured as follow. In the data and methods section, we first report the data cleaning and coding process and measurements used in our empirical analysis. Then we explain the rationale for choosing ordered beta regression to fit our models. In the Results section, we report and interpret both descriptive analysis and regression analysis results. We conclude the paper by discussing the implications of our findings with respective to more general scholarly understanding of the closing space of international civil society.

@@

The data used in this paper was collected from INGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for INGOs. We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparency of our analysis to broader communities. The data we collected spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 ROs in total. The filing document of ROs disclose the name, the registration date, the registration authority (which public security bureau regulates it), the PSU, the address and issue area or purposes of the RO and the specific provinces they can work in. We code the variables we use in the empirical analysis from the registration information. Most of the coding and data cleaning work is objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document. Meanwhile, the coding of issue areas are conducted by the authors based on the areas set out Article 3 (specified above) and clustering of the issue areas of the actually registered ROs.  (to cross-validate among authors).

@@

### Dependent Variables

Our dependent variable is "geo_scope_num", the count of the total number of provinces each RO is authorized to operate in. We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation. As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations. For example, in circumstances where emergency like the COVID 19 pandemic hits, it would be extremely hard for INGOs to plan beforehand which areas would need their service. Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such needs) be able to operate in as broader geographical scope as possible.

### Independent Variables

Our first independent variable is "work_field_code1", the issue area we code from mission statement specified in the RO's registration documentation. Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers (to do). The coding rules for overlapping issue areas can be found in the Appendix (to add). We decided to have 9 issue areas groups based on list of lawful fields of work specified by the Article 3 of the ONGO Law and how actual issue areas cluster for registered ROs.

Below is the list of issue areas INGOs' registered ROs are coded into.

- **Economy and trade**
- **Environment** (including animal protection)
- **Education** (including youth development)
- **Charity and humanitarian** poverty alleviation, disaster relief, etc., including rural development 
- **Science and technology**
- **Industry association**
- **Health**, public health and health care system support (professional training)
- **Arts and Culture** including sports and international culture exchange
- **General**, usually grant-making organizations, Or working on general international communication, including among governments, or working on multiple fields not overlapping

Our second variable is "time_elapsed". This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect. The longer the time elapsed since registration should be achieved by INGOs, it indicates that it took longer time for them to seek the content of both the PSU and Public Security Bureaus to be their supervisions or regulators and grant them legal identity.

### Control Variables

Our first control variable is "local_connet". It is a dichotomous variable indicating whether operating locally is built into the RO's mission. There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad. So we include this variable in our model to how having local connection is associated with the operational space of ROs as well as how the contentious level associates with operation space when we account for this factor.

We also cluster our 633 RO cases by the province where they are registered in our hierarchical Bayesian modeling. Thus, we account for any variance caused by the socioeconomic and institutional differences in various provinces of China. And the level province is the apporoiate level to cluster because all the ROs are registered at the provincial public security bureaus.

## Regression Model

@@

Before examining the posterior results of the statistical, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law. We use our data to explore (1) when INGOs registered, (2) what kinds of issues registered INGOs work on, and (3) how large of a geographic reach INGOs have.

@@

The ONGO Law officially came into effect on January 1, 2017, and as seen previously in @fig-registration-timeline, the first year of the law saw the greatest total number of registrations. In our third empirical expectation, we propose that these early registrants under the new law were both less of a threat to regime stability and a higher priority for bureaucratic processing, and thus should be registered in more provinces and have more geographic flexibility throughout the country. However, the results of our model support the *reverse* of this expectation. @fig-timing-preds-1 once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017. Organizations that registered in the first year are predicted to work in all provinces 41–46% of the time, and are predicted to work in two or more provinces 34–39% of the time. These early INGOs are the most likely to be registered in only one province and are predicted to do so 17–23% of the time. After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces. By the end of 2022—5 years after the ONGO Law took effect—the probability of national -level registration increases to 55–61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27–32%. These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17–22% of the time. @fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017. INGOs that register early are predicted to work in 17–22 provinces, while those that wait until 2022 are predicted to work in 21–28.

@@

>>>>

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
date: "2023-04-09"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas. We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in. China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
bibliography: references.bib
link-citations: true
---

@@

In the past decade, nearly 100 countries have proposed or enacted legal measures designed to restrict civil society [@ICNL:2021], and only 21% of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @Civicus:2023]. This global trend of closing or shrinking civic space [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016] has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020]. On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017. As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.

The purpose of this study is to empirically examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China since 2017, and in particular how the ONGO Law has shaped the operational space allowed for INGO operations in the country. By examining the *de facto* implementation of the law in addition to its formal *de jure* regulations, we provide a more comprehensive and data-based picture of the operational space for INGOs. By relying on representative empirical data from mainland China, our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies.

International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches. Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009]. Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018].

Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011]. However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs. Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, such as foundations, associations, and social service organizations [@Ye:2021]. Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on project investors' right to investment returns.

The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law. The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief (Article 3). The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs. Formal registration an RO with a legal identity and allows them to th maintain an ongoing present in the country, while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year. The law's registration requirements were strictly enforced—after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.

This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examings the association between INGO issue areas and the operational space granted to them in the country. Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)—a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province. We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].

In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs. domestic NGOs. We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law. We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data. We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.

# Theoretical background and expectations

::: {.callout-warning}
Apologies! This section is still *incredibly* drafty!
:::

China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016].  Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A few studies [@Jia:2017; @YeHuang:2018)] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

## The "closing space" phenomenon

Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].

Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]

## De jure vs. de facto implementation of civil society regulations

@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations—the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015]. See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]

::: {.content-hidden}

@@

## Empirical expectations

Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in. Since the level of contentiousness is also manifested by the level of difficulty they face while seeking lawful registration.

- **Expectation 1** (issue area): Because they are seen as less of a threat to regime stability, INGOs working on less contentious issues should be registered in more provinces

Relationships with PSUs are a critical part of the INGO registration process. No PSU is obligated to take on a supervisory role for an INGO, and interested organizations have to cultivate relationships with local officials. Accordingly, many of the INGOs we observe in our data either demonstrate close connections with local governmental authorities or frame their activities and services with a narrower geographic scope.

Using the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility and reach might not reflect reality. Some INGOs explicitly limit their operations to specific provinces, either because their programming is more tailored to local conditions, or because they do not feel a need to go through the longer process of obtaining national-level registration. Accordingly, we temper our issue area expectation with a measure of explicitly local purpose. Organizations that have no intention of registering nationally should be registered in fewer provinces:

- **Expectation 2** (local connections): Because they are explicitly focused on local issues, INGos with more local connections should be registered in fewer provinces

Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect:

- **Expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces

@@

The data used in this paper was collected from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office online service platform. The data spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 registered organizations. The filing documents for ROs disclose the name, the address, the registration date, the registration authority (which public security bureau regulates it), the PSU, the issue area or purposes of the RO, and the specific provinces they can work in. We merge our INGO data with additional data from ChinaFile, including English organization names, for the sake of transparency and accessibility.

We code the variables we use in the empirical analysis from the registration information. Most of our data cleaning work is an objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document. Meanwhile, the qualitative coding of issue areas is conducted by the authors

@@

### Dependent variable

Our dependent variable is the count of the total number of provinces each INGO is authorized to operate in. We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation. As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas would need their service. Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such need) be able to operate in as broad a geographical scope as possible.

### Independent variables

Our key independent variables correspond to each of our three empirical expectations. First we code each INGO's issue area based on its mission statement reported in its registration documentation. Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers—Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases. We include our coding rules for overlapping issue areas in the appendix (in the future). We categorize each organization into one of the following nine issue areas:

- **Economy and trade**
- **Environment** (including animal protection)
- **Education** (including youth development)
- **Charity and humanitarian** poverty alleviation, disaster relief, etc., including rural development 
- **Science and technology**
- **Industry association**
- **Health**, public health and health care system support (professional training)
- **Arts and Culture** including sports and international culture exchange
- **General**, usually grant-making organizations, or working on general international communication, including among governments, or working on multiple fields not overlapping

Our second variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally. There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad. We thus include this variable in our analysis to explore how having local connections is associated with the operational space of ROs.

Our final variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date. This indicates how long it took INGOs to seek the consent and supervisory authority of both a PSU and the Public Security Bureau and to complete all other necessary bureaucratic requirements.

## Multilevel Bayesian model

@@

Before examining the posterior results of our statistical model, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law. We use our data to explore (1) when INGOs registered, (2) what kinds of issues registered INGOs work on, and (3) how large of a geographic reach INGOs have.

@@

The ONGO Law officially came into effect on January 1, 2017, and as seen previously in @fig-registration-timeline, the first year of the law saw the greatest total number of registrations. In our third empirical expectation, we propose that these early registrants under the new law were both less of a threat to regime stability and a higher priority for bureaucratic processing, and thus should be registered in more provinces and have more geographic flexibility throughout the country. However, the results of our model support the *reverse* of this expectation. @fig-timing-preds-1 once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017. Organizations that registered in the first year are predicted to work in all provinces 41–46% of the time, and are predicted to work in two or more provinces 34–39% of the time. These early INGOs are the most likely to be registered in only one province and are predicted to do so 17–23% of the time. After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces. By the end of 2021—5 years after the ONGO Law took effect—the probability of national -level registration increases to 55–61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27–32%. These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17–22% of the time. @fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017. INGOs that register early are predicted to work in 17–22 provinces, while those that wait until 2021 are predicted to work in 21–28.

@@

::: {.callout-warning}
**Still TODO!**
:::
